Comparing Reinforcement Learning and Finite State Machine Agents in Real Time Strategy Games: Impact on Player Experience

### 2025-04-13 Paper/main.tex
Answered parts of the research methodology, and gathered more papers on zotero.

% The difference between academic and non academic literature is that academic literature is peer-reviewed, and is as such, more reliable and trustworthy
% than non-academic literature, which can easily be biased or contain false information. Academic literature can also be more in-depth and detailed, due to
% the high research standards and requirements of academic institutions, especially IEEE.

@@

% Research Questions:

% 1. How do RL and FSM AI opponents compare in terms of player experience in RTS games?
% 2. What are the key factors that influence player experience when playing against RL and FSM AI opponents in RTS games?
% 3. How do RL and FSM AI opponents impact player immersion in RTS games?

% Research objective:

% The objective for the research is to evaluate the impact of RL and FSM opponents in RTS games, and to determin their impact on player experience and immersion,
% and what are the key factors that cause this impact/infuence. This is to be done by creating a simple RTS game, and implementing both RL and FSM agents,
% and then conducting a play test experiment with players, where both groups will then be surveyed to gather data on their experience. Along with this,
% data gathered during the playtest through unity analytics will be used to measure player engagement and immersion.

Research Methodology goes here

>>>>

The difference between academic and non academic literature is that academic literature is peer-reviewed, and is as such, more reliable and trustworthy
than non-academic literature, which can easily be biased or contain false information. Academic literature can also be more in-depth and detailed, due to
the high research standards and requirements of academic institutions, especially IEEE.

@@

\subsection{Research Questions}

1. How do RL and FSM AI opponents compare in terms of player experience in RTS games?
2. What are the key factors that influence player experience when playing against RL and FSM AI opponents in RTS games?
3. How do RL and FSM AI opponents impact player immersion in RTS games?

\subsection{Research objectives}

The objective for the research is to evaluate the impact of RL and FSM opponents in RTS games, and to determin their impact on player experience and immersion,
and what are the key factors that cause this impact/infuence. This is to be done by creating a simple RTS game, and implementing both RL and FSM agents,
and then conducting a play test experiment with players, where both groups will then be surveyed to gather data on their experience. Along with this,
data gathered during the playtest through unity analytics will be used to measure player engagement and immersion.

\subsection{Suitable Methodology}

% TODO:

\subsection{Description of methodology, design, and approach}

Create a simple RTS game, and implement both RL and FSM agents. Conduct a deductive experiment, where players will be split into 2 groups,
where the first group will play against the FSM, fill out a questionnaire to gather data on their experience, and then play against the RL agent,
and again answer the questionnaire. The second group will do the same, but in reverse order, playing against the RL agent first, and then the FSM.
The end of each experiment's questionnaires will have an open ended question, where players can provide feedback on their experience,
which will be used to gather qualitative data on their experience. Qualitative data will be used to support the quantitative data gathered from
the questionnaires, as well as some in-game analytics and logs. This should help capture the more qualitative aspects of player experience,
while still keeping everything quantitative and measurable. This should help in answering the research questions, and in determining the validity
of the Hypothesis.

\subsection{Reflection on validity and reliability of the research design}

% TODO:

\subsection{Etical considerations}

Since the playtest will not be conducted on minors, and will not involve any sensitive or identifiable data, the main ethical considerations
would fall onto the type of content in the game, and if it is appropriate for the players. In this case, it will be a simple cartoon like game,
so there should not be any issues with this. The participants will be informed of the nature of the game and the study, and be required to
sign a consent form before participating, and will be free to withdraw at any time.
